### 2017-01-09 doc/manuscript.Rmd
Wrote up table captions

tab_qic <- tab('qic', 'caption here')
tab_basic <- tab('basic', 'caption here')
tab_tagfa <- tab('tagfa', 'caption here')
tab_gee <- tab('gee', 'caption here')

>>>>

tab_qic <- tab('qic', 'Comparison of GEE model fitness for variable selection using quasi-likelihood information criteria.')
tab_basic <- tab('basic', 'Basic characteristics of PROMISE participants at each of the 3 clinic visits.')
tab_tagfa <- tab('tagfa', 'Concentration (nmol/mL) and relative percent (mol%) values of triacylglycerol fatty acids in PROMISE participants at the baseline visit (2004-2006).')
tab_gee_unadj <- tab('gee_unadj', 'Raw estimates and confidence interval values for *time*-adjusted GEE models of the association of the triacylglycerol fatty acids (mol% and nmol/mL) and total clinically-measured TAG with insulin sensitivity and beta-cell function outcomes using the 6 year longitudinal data from the PROMISE cohort. Estimates represent a percent difference in the outcome per SD increase in the fatty acid. P-values were adjusted for the BH false discovery rate, with an asterisk (*) denoting a significant (p<0.05) association.')
tab_gee_adj <- tab('gee_adj', 'Raw estimates and confidence interval values for *fully*-adjusted GEE models of the association of the triacylglycerol fatty acids (mol% and nmol/mL) and total clinically-measured TAG with insulin sensitivity and beta-cell function outcomes using the 6 year longitudinal data from the PROMISE cohort. Variables controlled for were follow-up time, waist circumference, baseline age, ethnicity, sex, ALT, physical activity, and total NEFA. Estimates represent a percent difference in the outcome per SD increase in the fatty acid. P-values were adjusted for the BH false discovery rate, with an asterisk (*) denoting a significant (p<0.05) association.')
